---
title: "National Toxic Pollutants"
author: "Beck Addison"
date: "10.08.19"

output: github_document
---

###Objective 0

Tidy data.

```{r load-packages}
library(tidyverse)
library(readr)
library(janitor)
library(ggmap)
library(maps)
library(usethis)

tri2018 <- read_csv("data/tri_2018_us.csv")
tri2018 <- clean_names(tri2018)

usa <- map_data("usa")
```
###Objective 1

Determine the most common toxic pollutant in the US.

```{r count-toxins}
topten <- tri2018 %>%

  count(x30_chemical) %>%
  arrange(desc(n)) %>%
  slice(1:10) %>%
  right_join(., tri2018) %>%
  filter(n != "NA")

topten %>%
  ggplot(aes(x = reorder(x30_chemical, n), y = n, fill = x37_carcinogen)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(y = "Times Detected", x = "Chemical", fill = "Carcinogen")
```

###Objective 2

Develop a map showing the measurement locations of the top ten pollutants in the US.

```{r heat-map-top10}

topten %>%
  filter(x30_chemical == "LEAD" | x30_chemical == "NICKEL") %>%
  ggplot(aes(x13_longitude, x12_latitude, size = x54_on_site_release_total, color = x30_chemical
             )) +
  geom_point() +
  xlim(-125,-50) +
  labs(x = "", y = "", size = "Total Chemical Released", color = "Chemical") +
  theme_bw()
  
```

Questions: why is there a line running down the middle of the country? What is making the states past Texas so much less likely to have carcinogenic compound releases in the way that the East and Midwest see?

###Objective 3
```{r frequency-by-state}

```


